### 2020-10-15 priority-cp.tex

From the perspective of process calculus, commuting conversions behave strangely. Let us consider the commuting conversion for $\pcp{\tm{\recv{x}{y}{P}}}$:
\[
  \usingnamespace{pcp}
  (\kappa_{\parr})
  \quad
  \tm{\res{z}{z'}{(\ppar{\recv{x}{y}{P}}{Q})}}
  \red
  \tm{\recv{x}{y}{\res{z}{z'}{(\ppar{P}{Q})}}}
\]
As a result of $(\kappa_{\parr})$, $\pcp{\tm{Q}}$ becomes blocked on $\pcp{\tm{\labrecv{x}{y}}}$, and any actions $\pcp{\tm{Q}}$ was able to perform become unavailable. Consequently, CP is non-confluent. For instance,
\begin{mathpar}
  \usingnamespace{pcp}
  \setlength{\arraycolsep}{2em}
  \begin{array}{cc}
    \multicolumn{2}{c}{%
    \hspace*{10ex}
    {\tm{\res{x}{x'}{(\ppar{\recv{a}{y}{P}}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
    \\
    \qquad\rotatebox[origin=c]{215}{$\red$}
    &
    \rotatebox[origin=c]{325}{$\red^2$}\qquad
    \\
    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
    &
    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{Q})}}}}
  \end{array}
\end{mathpar}
Commuting conversions break our intuition that an action with lower priority occurs before an action with higher priority, since ``if a prefix on a channel endpoint $\pcp{\tm{x}}$ with priority $\cs{o}$ is pulled out at top level, then to preserve priority conditions in the typing rules [..], it is necessary to increase priorities of all actions after the prefix on $\pcp{\tm{x}}$'' by $\cs{o+1}$~\cite{dardhagay18}.

@@

\subsubsection*{Operational Semantics}
The operational semantics for PCP, given in \cref{fig:pcp-operational-semantics}, is defined as a reduction relation $\pcp{\red}$ on processes (bottom) and uses structural congruence (top). Each of the axioms of structural congruence corresponds to the axiom of the same name for PGV.\simon{Maybe worth highlighting that it is an internal mobility calculus, for the pi calculus people.}

>>>>

From the perspective of process calculus, commuting conversions behave strangely. Let us consider the commuting conversion for $\pcp{\tm{\recv{x}{y}{P}}}$:
\[
  \usingnamespace{pcp}
  (\kappa_{\parr})
  \quad
  \tm{\res{z}{z'}{(\ppar{\recv{x}{y}{P}}{Q})}}
  \red
  \tm{\recv{x}{y}{\res{z}{z'}{(\ppar{P}{Q})}}}
\]
As a result of $(\kappa_{\parr})$, $\pcp{\tm{Q}}$ becomes blocked on $\pcp{\tm{\labrecv{x}{y}}}$, and any actions $\pcp{\tm{Q}}$ was able to perform become unavailable. Consequently, CP is non-confluent. For instance,
\begin{mathpar}
  \usingnamespace{pcp}
  \setlength{\arraycolsep}{2em}
  \begin{array}{cc}
    \multicolumn{2}{c}{%
    \hspace*{10ex}
    {\tm{\res{x}{x'}{(\ppar{\recv{a}{y}{P}}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
    \\
    \qquad\rotatebox[origin=c]{215}{$\red$}
    &
    \rotatebox[origin=c]{325}{$\red^+$}\qquad
    \\
    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
    &
    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{Q})}}}}
  \end{array}
\end{mathpar}
Commuting conversions break our intuition that an action with lower priority occurs before an action with higher priority, since ``if a prefix on a channel endpoint $\pcp{\tm{x}}$ with priority $\cs{o}$ is pulled out at top level, then to preserve priority conditions in the typing rules [..], it is necessary to increase priorities of all actions after the prefix on $\pcp{\tm{x}}$'' by $\cs{o+1}$~\cite{dardhagay18}.

@@

\subsubsection*{Operational Semantics}
The operational semantics for PCP, given in \cref{fig:pcp-operational-semantics}, is defined as a reduction relation $\pcp{\red}$ on processes (bottom) and uses structural congruence (top). Each of the axioms of structural congruence corresponds to the axiom of the same name for PGV. We write $\pcp{\red^+}$ for the transitive closures, and $\pcp{\tred^\star}$ for the reflexive-transitive closures.\simon{Maybe worth highlighting that it is an internal mobility calculus, for the pi calculus people.}

### 2020-10-15 priority-gv.tex

\subsubsection*{Example}\label{sec:pgv-example}
Suppose a set of processes $\tm{\proc{i}}$, $1\leq{i}\leq{n}$, should be scheduled to perform some tasks in cyclic order, starting with $\tm{\proc0}$, and circling all the way around to $\tm{\proc{n}}$, notifying $\tm{\proc0}$ when every other process has finished their task.

>>>>

\subsubsection*{Example}\label{sec:pgv-example}
Suppose a set of processes $\tm{\proc{i}}$, $1\leq{i}\leq{n}$, should be scheduled to perform some tasks in cyclic order, starting with $\tm{\proc0}$, ending with $\tm{\proc{n}}$, and notifying $\tm{\proc0}$ when all processes have finished.
